\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{enumitem}

\setstretch{1.15}
\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\begin{document}

\begin{center}
\Large\textbf{DAY 1 DEFENSE PACKET}\\[0.5em]
\large\textbf{People v. SULLIVAN, JOHN DILLON}\\[0.25em]
\textbf{Sonoma County Superior Court, Case No. 25CR03297}
\end{center}

\vspace{1em}

\noindent
\textbf{Prepared for:} John{-}Dillon:Sullivan, a living man\\
\textbf{Prepared by:} Private Defense Support\\
\textbf{Date:} \underline{\hspace{2cm}}

\section*{Document Structure}

\begin{enumerate}[label=\arabic*.]
  \item FDIC Depositor Rights Assertion \& Records Demand (Summary Reference)
  \item Affidavit of Status \& Rebuttal of Constructive Attribution
  \item Motion to Strike / Demurrer for Lack of Jurisdiction and Insufficient Complaint
  \item Arrest Packet \& Evidence Analysis (Sonoma / Santa Rosa 4--23--2025)
  \item Court Docket / Minutes Analysis (Case No. 25CR03297)
  \item Inconsistency \& Chain-of-Custody Audit
  \item Bench Script (Spoken Record at Hearings)
\end{enumerate}

\newpage
\section{Affidavit of Status and Rebuttal of Constructive Attribution}

\noindent
\textbf{Affidavit of John{-}Dillon{:}Sullivan, a Living Man}\\[0.5em]
In Honor, Without Prejudice, All Rights Reserved

\vspace{0.5em}

\noindent
I, John{-}Dillon{:}Sullivan, being of sound mind and competent, declare under penalty of perjury as follows:

\subsection*{1. Status}

\begin{enumerate}[label*=\arabic*.]
  \item I am a living man, created by the Divine, not a corporate entity, fiction, vessel, or other creature of statute.
  \item I do not consent to be identified as, or treated as surety or trustee for, the all{-}capitalized en legis designation ``JOHN DILLON SULLIVAN'' or any similar legal construct.
\end{enumerate}

\subsection*{2. Notice of Attribution Rules}

\begin{enumerate}[label*=\arabic*.]
  \item In American jurisprudence, liability or ownership may be attributed ``constructively'' through doctrines including attribution rules in federal tax law, alter ego, and veil piercing.
  \item Such doctrines require proof that one party used another entity for benefit, control, or concealment of liability; mere similarity of name is not sufficient.
\end{enumerate}

\subsection*{3. Limitation of Attribution}

\begin{enumerate}[label*=\arabic*.]
  \item I have not used any en legis designation in my name for concealment, fraud, or evasion.
  \item No party has produced competent evidence that obligations of any such entity should be attributed to me, the living man.
  \item Constructive attribution is a rebuttable legal presumption. I hereby rebut any presumption that I, as a living man, automatically inherit the debts, liabilities, or obligations of any artificial entity styled in my name.
\end{enumerate}

\subsection*{4. Separation of Capacities}

\begin{enumerate}[label*=\arabic*.]
  \item If any court or agency treats the all{-}caps designation as a trust, I claim the position of beneficiary and do not accept appointment as surety or trustee without my express written consent.
  \item If such designation is treated as a corporate or administrative vessel, I do not accept any office, directorship, agency, or suretyship therein unless expressly and knowingly contracted.
\end{enumerate}

\subsection*{5. Demand for Proof of Nexus}

\begin{enumerate}[label*=\arabic*.]
  \item Any party asserting that I am bound as surety or trustee for the en legis entity shall be required to produce:
  \begin{enumerate}[label*=\alph*.]
    \item A signed contract or instrument showing my voluntary acceptance of that role; and
    \item Evidence that I exercised control, received benefit, or used the entity to conceal liability.
  \end{enumerate}
\end{enumerate}

\subsection*{6. Declaration}

\noindent
I declare under penalty of perjury under the laws of the State of California that the foregoing is true and correct to the best of my knowledge and belief.

\vspace{2em}
\noindent
\textbf{Executed on:} \underline{\hspace{3cm}} at \underline{\hspace{4cm}}, California.\\[2em]
\textbf{By:} \rule{7cm}{0.4pt}\\
John{-}Dillon{:}Sullivan, a living man

\newpage
\section{Motion to Strike / Demurrer for Lack of Jurisdiction and Insufficient Complaint}

\noindent
\textbf{SUPERIOR COURT OF CALIFORNIA, COUNTY OF SONOMA}\\[0.25em]
\textbf{THE PEOPLE OF THE STATE OF CALIFORNIA}, Plaintiff,\\
v.\\
\textbf{SULLIVAN, JOHN DILLON}, Defendant.\\[0.25em]
Case No. 25CR03297

\vspace{0.5em}

\noindent
\textbf{SPECIAL APPEARANCE MOTION TO STRIKE AND DEMURRER}\\
\textbf{FOR LACK OF JURISDICTION AND FAILURE TO STATE FACTS}\\
\textbf{SUFFICIENT TO CONSTITUTE AN OFFENSE}

\vspace{0.5em}

\noindent
Comes now John{-}Dillon{:}Sullivan, a living man, appearing in propria persona and by special appearance only, and moves this Court to strike the operative complaint and, in the alternative, demurs under Code of Civil Procedure section 430.10 and applicable criminal pleading standards, on the following grounds:

\subsection{Ground 1: Misidentification and Capacity}

\begin{enumerate}[label*=\arabic*.]
  \item The caption and minutes identify the defendant as ``SULLIVAN, JOHN DILLON'' in all capital letters.
  \item No competent evidence has been presented establishing that this en legis designation is identical in legal capacity to the living man appearing before the Court.
  \item Jurisdiction over a party requires proper identification and service upon the correct person or entity; misidentification undermines personal jurisdiction.
\end{enumerate}

\subsection{Ground 2: Insufficient Factual Allegations}

\begin{enumerate}[label*=\arabic*.]
  \item The original and first amended complaints allege, among other counts, conspiracy under Penal Code section 182(a)(1) and petty theft with prior under Penal Code section 666.1(a)(1).
  \item The conspiracy count recites generic elements and lists overt acts but fails to particularize which acts were allegedly committed by Mr.\ Sullivan, as distinct from alleged co{-}actors, contrary to California pleading requirements for a ``simple, concise, and direct statement of the facts'' sufficient to apprise the accused of the specific conduct charged.
  \item The petty theft with prior enhancement alleges prior convictions without attaching certified abstracts of judgment or other admissible proof of those priors, as required when pleading sentence enhancements based on prior convictions.
\end{enumerate}

\subsection{Ground 3: Jurisdictional Defects and Dismissed Counts}

\begin{enumerate}[label*=\arabic*.]
  \item According to the court's own minutes in Case No.\ 25CR03297, the counts for conspiracy (Count 001) and petty theft with two or more priors (Count 002) have been dismissed on motion of the People.
  \item To the extent any remaining proceedings, plea negotiations, or settlement conferences rely on these dismissed felony counts for leverage or exposure,
documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{perplexity}
\author{JOHN DILLON SULLIVAN}
\date{December 2025}

\begin{document}

\maketitle

\section{Introduction}

\end{document}
